Numerous variables relating to 2016 election in 2021 US GSS

### 2022-03-18 outputs/paper/paper.Rmd
..
ggplot cleaning

```{r}
library(ggplot2)
reduced_data %>%
  ggplot(aes(x = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = gender)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = race)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = gender, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = degree, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = born_US, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = Family_income, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = nation_education, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = nation_race, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = nation_arms, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = nation_welfare, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = Assistance_to_the_poor, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = Assistance_to_other_countries, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = social_security, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = race, fill = pres16)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = degree, fill = Family_income)) +
  geom_bar()

@@

3.

>>>>

```{r}
library(ggplot2)
library(dplyr)
reduced_data %>%
  ggplot(aes(x = age, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data$pres16 <- factor(reduced_data$pres16, levels = c("Clinton","Trump","Other","Did not vote"))
reduced_data %>%
  ggplot(aes(x = pres16, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = gender, fill = gender)) +
  geom_bar() +
  scale_fill_brewer(palette = "Blues")

reduced_data %>%
  ggplot(aes(x = race, fill = race)) +
  geom_bar() +
  scale_fill_brewer(palette = "yellow")

reduced_data %>%
  ggplot(aes(x = gender, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = born_US, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data$Family_income <- factor(reduced_data$Family_income, levels = c("Under $10,000","$10,000 ~ $19,999","$20,000 ~ $39,999","$40,000 ~ $59,999","$60,000 ~ $89,999","$90,000 ~ $129,999","$130,000 ~ $169,999","$170,000 or over"))
reduced_data %>%
  ggplot(aes(x = Family_income, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate") +
  coord_flip()

reduced_data %>%
  ggplot(aes(x = nation_education, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = nation_race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = nation_arms, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = nation_welfare, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = Assistance_to_the_poor, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = Assistance_to_other_countries, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = social_security, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(Family_income, levels = c("$170,000 or over","$130,000 ~ $169,999","$90,000 ~ $129,999","$60,000 ~ $89,999","$40,000 ~ $59,999","$20,000 ~ $39,999","$10,000 ~ $19,999","Under $10,000")))) +
  geom_bar() +
  labs(fill = "Family Income") +
  coord_flip()

@@
